---
title:  "Efficient Fuel Consumption Analysis"
output: pdf_document
---

## Executive Summary

Based in the data gathered by _Motor Trend US_ magazine in 1974, this study concludes than manual transmission is more efficient than automatic transmission, with 7.25 ($\pm$ 1.75) more miles per gallon, but only the 36% of variations of yield in terms of mpg are explained by transmission type. A more accuracy model must include variables such as weight, 1/4 mille time, displacement (cubic inch) and horse power, additional to transmission type.

## Exploratory Data Analysis

Looking at a data set of a collection of cars, _Motor Trend_, a magazine about the automobile industry, is interested in exploring the relationship between a set of variables and miles per gallon (MPG). They are particularly interested in the following two questions:

* "Is an automatic or manual transmission better for MPG?"
* "Quantify the MPG difference between automatic and manual transmissions"

The data was extracted from the 1974 _Motor Trend US_ magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models). The detail of all aspects included can be found [here](http://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html). See Figure 1 in appendix for a matrix plot of `mtcars` dataset.

```{r LoadData, echo=FALSE}
  data(mtcars)
```

```{r Head_MTcars}
  head(mtcars)
```

### Data Analysis

The first aspect to be evaluated: "Is an automatic or manual transmission better for MPG?", suggest a hypothesis test:

* H~0~ (null hypothesis): There is no differerence between automatic and manual transmission in terms of MPG
* H~a~ (alternative hypothesis): There are differences between automatic and manual transmission in terms of MPG

```{r T_Test, echo=FALSE}

  mtdata      <- mtcars

  mtdata$cyl  <- factor(mtdata$cyl)
  mtdata$vs   <- factor(mtdata$vs, labels=c("V", "S"))
  mtdata$am   <- factor(mtdata$am, labels=c("Automatic", "Manual"))
  mtdata$gear <- factor(mtdata$gear)
  mtdata$carb <- factor(mtdata$carb)

  mpg.at <- mtdata[mtdata$am == "Automatic", ]$mpg
  mpg.mt <- mtdata[mtdata$am == "Manual",    ]$mpg

  at.mt.test <- t.test(mpg.at, mpg.mt, paired=FALSE, conf.level = 0.95)

```

After executing a Student's t-test with a confidence level of 95%, the resulting p-value, `r round(at.mt.test$p.value * 100, 2)`%, less than 5% (or even 1%), allow us to reject H~0~, indicating that there are differences between automatic and manual transmission, in terms of MPG. Now, we have to quantify this difference.   
   
### Regression Model

Lets generate a linear model with _mpg_ as output and _transmission type_ as predictor:

```{r}
  fit <- lm(mpg ~ factor(am), data=mtcars)
```

```{r , echo=FALSE}
  fit2 <- lm(mpg ~ factor(am) - 1, data=mtcars)  # Read manual transmission data directly
```

Results indicate the following:

* Mean of automatic transmission is `r round(summary(fit)$coefficients[1, 1], 3)` $\pm$ `r round(summary(fit)$coefficients[1, 2], 3)` mpg
* Mean of manual transmission is `r round(summary(fit2)$coefficients[2, 1], 3)` $\pm$ `r round(summary(fit2)$coefficients[2, 2], 3)` mpg
* Manual transmission vehicles have a yield of `r round(summary(fit)$coefficients[2, 1], 3)` $\pm$ `r round(summary(fit)$coefficients[2, 2], 3)` mpg more in relation to vehicles with automatic transmission
* Only the `r round(summary(fit)$r.squared * 100, 0)`% of variations of yield in terms of mpg are explained by the transmission type, so we have to find a more accurate model.

## Model Selection

After using a _brut-force approach_, evaluating all possible combinations of predictors and selecting the combination which maximizes adjusted $R^2$ (see Figure 3), we get the following model:

```{r LinearModels, echo=FALSE, cache=TRUE}
  data(mtcars)
  R2 <- data.frame(adj.r2=summary(lm(mpg ~ carb, data=mtcars))$adj.r.square, model='mpg ~ carb', stringsAsFactors=FALSE)
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ gear, data=mtcars))$adj.r.square, model='mpg ~ gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ gear + carb, data=mtcars))$adj.r.square, model='mpg ~ gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ am, data=mtcars))$adj.r.square, model='mpg ~ am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ am + carb, data=mtcars))$adj.r.square, model='mpg ~ am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ am + gear, data=mtcars))$adj.r.square, model='mpg ~ am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ vs, data=mtcars))$adj.r.square, model='mpg ~ vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ vs + carb, data=mtcars))$adj.r.square, model='mpg ~ vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ vs + gear, data=mtcars))$adj.r.square, model='mpg ~ vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ vs + am, data=mtcars))$adj.r.square, model='mpg ~ vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec, data=mtcars))$adj.r.square, model='mpg ~ qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + am, data=mtcars))$adj.r.square, model='mpg ~ qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt, data=mtcars))$adj.r.square, model='mpg ~ wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + gear, data=mtcars))$adj.r.square, model='mpg ~ wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + am, data=mtcars))$adj.r.square, model='mpg ~ wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + vs, data=mtcars))$adj.r.square, model='mpg ~ wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat, data=mtcars))$adj.r.square, model='mpg ~ drat'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + am, data=mtcars))$adj.r.square, model='mpg ~ drat + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + am + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + am + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + vs, data=mtcars))$adj.r.square, model='mpg ~ drat + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + vs + am, data=mtcars))$adj.r.square, model='mpg ~ drat + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt, data=mtcars))$adj.r.square, model='mpg ~ drat + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + am, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ drat + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ drat + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp, data=mtcars))$adj.r.square, model='mpg ~ hp'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + am, data=mtcars))$adj.r.square, model='mpg ~ hp + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + vs, data=mtcars))$adj.r.square, model='mpg ~ hp + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + vs + am, data=mtcars))$adj.r.square, model='mpg ~ hp + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt, data=mtcars))$adj.r.square, model='mpg ~ hp + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + am, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat, data=mtcars))$adj.r.square, model='mpg ~ hp + drat'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + am, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + vs, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + vs + am, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + am, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ hp + drat + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ hp + drat + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp, data=mtcars))$adj.r.square, model='mpg ~ disp'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + am, data=mtcars))$adj.r.square, model='mpg ~ disp + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt, data=mtcars))$adj.r.square, model='mpg ~ disp + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + am, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat, data=mtcars))$adj.r.square, model='mpg ~ disp + drat'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + am, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + am, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + drat + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + drat + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp, data=mtcars))$adj.r.square, model='mpg ~ disp + hp'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ disp + hp + drat + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ disp + hp + drat + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl, data=mtcars))$adj.r.square, model='mpg ~ cyl'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + drat + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + drat + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + hp + drat + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + hp + drat + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + drat + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + drat + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + wt + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + qsec + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + vs + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + am + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + vs, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + vs'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + vs + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + vs + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + vs + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + vs + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + vs + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + vs + gear + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + vs + am, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + vs + am'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + vs + am + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + vs + am + carb'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + vs + am + gear, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + vs + am + gear'))
  R2 <- rbind(R2, data.frame(adj.r2=summary(lm(mpg ~ cyl + disp + hp + drat + wt + qsec + vs + am + gear + carb, data=mtcars))$adj.r.square, model='mpg ~ cyl + disp + hp + drat + wt + qsec + vs + am + gear + carb'))

```

```{r , echo=FALSE, eval=FALSE}

# Evaluate the first 5 models according to decreasing adjusted R2
  head(R2[order(R2$adj.r2, decreasing=TRUE), ], 5)
  
  model1 <- lm(mpg ~ disp + hp +        wt + qsec + am,        data=mtcars)
  model2 <- lm(mpg ~        hp +        wt + qsec + am,        data=mtcars)
  model3 <- lm(mpg ~                    wt + qsec + am + carb, data=mtcars)
  model4 <- lm(mpg ~ disp + hp + drat + wt + qsec + am,        data=mtcars)
  model5 <- lm(mpg ~ disp + hp +        wt + qsec + am + gear, data=mtcars)
  
  anova(model1, model2, model3, model4, model5)

```

```{r BestFitModel, echo=FALSE}

  best.fit <- lm(mpg ~ disp + hp + wt + qsec + am, data=mtcars)

  best.fit$call
```

Figure 4 shows the residual plots of the selected model, which we can observe the following:

* The points in _Residuals vs Fitted_ plot are randomly scattered with no particular pattern, but regression line indicates other predictors not included in the original data influence fuel consumption (way of driving, city or highway driving, etc.)
* The points in _Normal Q-Q_ plot are quite aligned, indicating that the residuals follow a normal distribution.
* In both, _Scale-Location_ and _Residuals vs Leverage_ plots, the points are in a group with none too far from the center.

## Conclusion

* Manual transmission is more efficient than automatic transmission, with `r round(summary(fit)$coefficients[2, 1], 3)` ($\pm$ `r round(summary(fit)$coefficients[2, 2], 3)`) more miles per gallon.
* Transmission type is not the only variable which explains gas comsumption (just `r round(summary(fit)$r.squared * 100, 1)`% of variations)
* Selected model (transmission type, weight, 1/4 mille time, displacement and horse power) explains `r round(summary(best.fit)$r.squared * 100, 1)`% of variations.
* There are other predictors not included in the original data influence fuel consumption. 

## Appendix

### Figure 1. Matrix of plots of **mtcars** dataset

```{r Figure1, echo=FALSE}

  library (GGally)
  library(ggplot2)

  ggpairs(mtcars,
          upper = list(params = c(size = 3)),
          lower = list(continuous = "smooth",
                       params = c(method = "loess")),
          axisLabels="none")

```

### Figure 2. MPG according to Transmission type

```{r Figure2, echo=FALSE, fig.height=5, fig.width=5}

  ggplot(mtdata, aes(am, mpg)) +
    geom_boxplot() +
    xlab("Transmission type")
```

### Figure 3. Adjusted $R^2$ for all evaluated models

```{r Figure3, echo=FALSE}
  ggplot(R2, aes(x=1:nrow(R2), y=R2$adj.r2)) +
    xlab("Model") +
    ylab("adj.r2") +
    geom_line(col="darkgray") +
    geom_point() +
    geom_point(aes(x=which(R2$adj.r2 == max(R2$adj.r2)), y=max(R2$adj.r2)),
               pch=19, col="red", size=3) +
    geom_text(aes(x=which(R2$adj.r2 == max(R2$adj.r2)) - 30, y=0.575),
              label=paste("Model = ", R2$model[which(R2$adj.r2 == max(R2$adj.r2))]),
              hjust=0, col="darkblue", size=4) +
    geom_text(aes(x=which(R2$adj.r2 == max(R2$adj.r2)) - 30, y=0.635),
             label=paste("Max Adjusted R^2 = ", round(R2$adj.r2[which(R2$adj.r2 == max(R2$adj.r2))], 5)),
             hjust=0, col="darkblue", size=4)

```

### Figure 4. Residuals plots of selected model

```{r Figure4, echo=FALSE}

  par(mfrow = c(2,2))
  plot(best.fit)

```

### Aditional information

See [GitHub repository]() for source file of this report and the worksheet used to build linear models combinations.
